% BSD 3-Clause License
%
% Copyright (c) 2023 Quux System and Technology. All rights reserved.
%
% Redistribution and use in source and binary forms, with or without
% modification, are permitted provided that the following conditions are met:
%
% 1. Redistributions of source code must retain the above copyright notice, this
%    list of conditions and the following disclaimer.
%
% 2. Redistributions in binary form must reproduce the above copyright notice,
%    this list of conditions and the following disclaimer in the documentation
%    and/or other materials provided with the distribution.
%
% 3. Neither the name of the copyright holder nor the names of its
%    contributors may be used to endorse or promote products derived from
%    this software without specific prior written permission.
%
% THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS "AS IS"
% AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE
% IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE ARE
% DISCLAIMED. IN NO EVENT SHALL THE COPYRIGHT HOLDER OR CONTRIBUTORS BE LIABLE
% FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL
% DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR
% SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION) HOWEVER
% CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY,
% OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE
% OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
%
\begin{recipe}[八宝糯米鸡]{糯米鸡}

\ingredients

\ingredient{仔母鸡一只}{约三斤}
\ingredient{鲜豌豆仁}{二两五}
\ingredient{糯米}{二两}
\ingredient{熟火腿}{六钱}
\ingredient{金钩}{三钱}
\ingredient{水发香菌}{六钱}
\ingredient{苡仁}{二钱}
\ingredient{莲米}{三钱}
\ingredient{鸡蛋清}{一个}
\ingredient{香油}{三钱}
\ingredient{盐}{四分}
\ingredient{酱油}{六钱}
\ingredient{椒盐面}[\footnotemark]{二钱}
\ingredient{干豆粉}{五钱}
\ingredient{芡实}{二钱}
\ingredient{菜油}{二斤约耗二两}
\ingredient{胡椒}{一分}

\preparation

\step 仔母鸡一只宰杀后放净血，去掉毛、足，从鸡背颈部上面，顺割约三寸长的口，用
手挖去鸡膆，仰放在菜墩上，用刀从杀口处将鸡颈骨割断，再从鸡背颈刀口处将颈骨拉
出。然后将鸡立放在菜墩上，用手将鸡皮肉略为用力向外翻，并向下褪，鸡骨架就逐渐露
出。鸡翅膀与胸腔骨相连的筋用刀割断，随顺着鸡的肉骨周围相连地方慢慢往下剐，边褪
边剐，直剐到鸡的尾部，把鸡的骨架内脏取出。再用刀尖拨开鸡的两腿棒子骨，使棒子骨
露出一点，两手用力将鸡腿肉往下按，棒子骨就全部露出，用刀剔下。此时鸡除头部、两
翅外，骨头都已剔下（剔剐过程中，注意保持肉皮完整无破损）。再将鸡皮面翻出来，在
清水中洗干净，滤干水份。

\step 鲜豌豆仁用沸水煮熟去壳，漂在清水中，保持绿色。糯米淘洗后在沸水锅内煮透，
以尚未成饭、米无硬心为度。莲米（退衣去心）、苡仁和芡实淘洗后用开水泡胀，装在碗
内，加清水泡浸，上笼蒸𤆵。金钩用沸汤泡胀，与香菌、火腿切成如豌豆大小的丁，然后
将鲜豌豆仁、糯米、莲米、苡仁、芡实、金钩、香菌和火腿加盐拌匀，从鸡颈开口处装入
腹内，装好后用削细的竹签（约五寸长）像缝衣似的将鸡颈开口处锁住（从外面看如同一
只有骨的鸡），放入沸汤锅中烫一下捞出，将鸡翅翻在背上盘起，鸡头仰翻在翅的下面压
住，再装入大蒸碗内，鸡背向上，不加水上笼干蒸；蒸约两小时，用竹筷以能将鸡翅戳破
为适合，然后把它翻入盘内，用干布帕将鸡身的水气沾干，全身抹上酱油；再将鸡蛋加干
豆粉搅打成蛋清豆粉抹上。

\step 大炒锅内放入菜油，在旺火上烧至八成热时，即将鸡顺着锅边放入，腹部向上（向
下容易炸糊）炸五分钟；炸时用汤瓢将鸡不断拨动，并圈沸油往鸡腹上不断浇淋；待鸡身
炸成金黄色时滗去炸油，淋入香油起锅。随后用刀将腹部轻轻划成象眼块，以将皮划断为
度，不可深及肉内。上盘时抽、掉颈部竹签，随同椒盐二碟上席。

\features

此鸡颜色金黄光亮，大方美观，皮酥肉嫩，酿馅鲜香，风味特佳。

\footnotetext{
椒盐是盐和花椒面拌合而成，配比是一比二。
}

\end{recipe}

% vim: filetype=tex noautoindent nojoinspaces
% vim: fileencoding=utf-8 formatoptions+=m
% vim: textwidth=78 tabstop=4 shiftwidth=4 softtabstop=4
