% BSD 3-Clause License
%
% Copyright (c) 2023 Quux System and Technology. All rights reserved.
%
% Redistribution and use in source and binary forms, with or without
% modification, are permitted provided that the following conditions are met:
%
% 1. Redistributions of source code must retain the above copyright notice, this
%    list of conditions and the following disclaimer.
%
% 2. Redistributions in binary form must reproduce the above copyright notice,
%    this list of conditions and the following disclaimer in the documentation
%    and/or other materials provided with the distribution.
%
% 3. Neither the name of the copyright holder nor the names of its
%    contributors may be used to endorse or promote products derived from
%    this software without specific prior written permission.
%
% THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS "AS IS"
% AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE
% IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE ARE
% DISCLAIMED. IN NO EVENT SHALL THE COPYRIGHT HOLDER OR CONTRIBUTORS BE LIABLE
% FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL
% DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR
% SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION) HOWEVER
% CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY,
% OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE
% OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
%
\begin{recipe}{樟茶鸭子}

\ingredients

\ingredient{肥公鸭一只}{三斤}
\ingredient{味精}{二分}
\ingredient{醪糟}{一两}
\ingredient{花茶}{一两}
\ingredient{香樟树叶}{一两}
\ingredient{葱}{二两五}
\ingredient{香油}{二钱}
\ingredient{花椒}{约二十粒}
\ingredient{胡椒面}{一钱}
\ingredient{料酒}{一两}
\ingredient{菜油}{二斤耗二两}
\ingredient{甜酱}{一钱}
\ingredient{盐}{一两}
\ingredient{硝}{一钱}
\ingredient{柏枝}{四两}
\ingredient{锯末}{四两}

\preparation

\step 将鸭宰杀去毛，清洗干净，再用铁皮夹子摘净茸毛，然后放于案板上，用刀在颈项
上接近鸭背处开一口，长约一寸，由此处将鸭的软喉及鸭膆扯出。再在鸭背离尾部尽头处
横割一刀，约二寸长，由此刀口中将鸭的脏腹挖取干净，再用水洗净，晾干水。葱去叶和
须，用葱白，切成一寸半长的段，盛盘中待用。

\step 用碗将花椒、盐、胡椒面拌匀，抹于鸭腹之中。再将料酒和醪糟拌匀，涂在鸭皮
上。余下的抹于鸭腹之中。然后将鹎放盆内醃十二小时，晾干水。

\step 将花茶、锯末、柏枝、香樟树叶一起和匀，平均分为三份。把木盆一个（高约四寸
）放平地上，将茶叶、锯末等一份，放入一土碗中，再从炉内夹一段烧红的炭放在茶叶、
锯末上面，将碗放入木盆中央。木盆口上平放一张稀眼铁丝网，鸭子放铁丝网上，另用大
盆一个盖着，用茶叶锯末所燃起的烟熏。熏十分钟后，揭开大盆，取出土碗，加茶叶锯末
一份，另换烧红炭一段放回盆中，将鸭翻过来，盖上大盆，再熏七分钟。然后再将大盆揭
开，取出土碗，将余下一份茶叶锯末放入，另换红炭，将碗放入木盆中，再将鸭色浅的一
面向下，盖上大盆熏五分钟。此时鸭色呈现出深黄色，将鸭取出，放入大蒸碗中，上笼蒸
三小时，出笼晾冷待用。

\step 锅放炉上，倒入菜油烧热，再将鸭放入炸五分钟，至鸭皮已酥捞出。将鸭放于案板
上，先剁下鸭颈，切成六分长的段，放于大圆盘中央；再将鸭身劈成两半，每半顺切成两
块，再横切成一寸宽的块，鸭皮向上盖于盘中鸭颈块上，并将鸭摆成原形。

\step 香油一钱与甜酱拌匀，平均分成二份，分别摆在盛鸭的条盘两端。葱白段亦分成二
份，照甜酱摆法摆入盘中，再将余下的香油淋于鸭块上上席。

\features

此菜经过醃、熏、蒸、炸四个过程，因而具有酥、香、𤆵、嫩的特点，并且带有茶叶和
樟树叶的特种香味；颜色亦很艳丽。最宜下酒。随荷叶饼、花卷同吃。

\end{recipe}

% vim: filetype=tex noautoindent nojoinspaces
% vim: fileencoding=utf-8 formatoptions+=m
% vim: textwidth=78 tabstop=4 shiftwidth=4 softtabstop=4
