% BSD 3-Clause License
%
% Copyright (c) 2023 Quux System and Technology. All rights reserved.
%
% Redistribution and use in source and binary forms, with or without
% modification, are permitted provided that the following conditions are met:
%
% 1. Redistributions of source code must retain the above copyright notice, this
%    list of conditions and the following disclaimer.
%
% 2. Redistributions in binary form must reproduce the above copyright notice,
%    this list of conditions and the following disclaimer in the documentation
%    and/or other materials provided with the distribution.
%
% 3. Neither the name of the copyright holder nor the names of its
%    contributors may be used to endorse or promote products derived from
%    this software without specific prior written permission.
%
% THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS "AS IS"
% AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE
% IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE ARE
% DISCLAIMED. IN NO EVENT SHALL THE COPYRIGHT HOLDER OR CONTRIBUTORS BE LIABLE
% FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL
% DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR
% SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION) HOWEVER
% CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY,
% OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE
% OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
%
\begin{recipe}{黄焖大鲢鱼头}[\footnotemark]

\ingredients

\ingredient{鲢鱼头}{一个约四五斤}
\ingredient{猪肥膘肉}{五两}
\ingredient{料酒}{六两}
\ingredient{酱油}{二两}
\ingredient{葱白}{二两}
\ingredient{大蒜（去皮蒸𤆵）}{五两}
\ingredient{咸红酱油}{八钱}
\ingredient{白菌菰}{一两}
\ingredient{姜}{四钱}
\ingredient{金钩}{六钱}
\ingredient{鸡汤}{四斤}
\ingredient{冰糖（砸碎）}{六钱}
\ingredient{鸡足鸭掌}{四对}
\ingredient{化猪油}{一斤耗二两五}

\preparation

\step 大鲢鱼头一个，挖去鳃，去掉牙板骨，在水中清洗干净；对准鱼口从脑顶骨中砍
开，不要砍断。鸡足鸭掌洗干净，在开水锅内紧一下，去掉粗皮。白菌菰用清水泡半小
时，待菌已开始胀，用手刮洗去泥沙，再在沸水锅内煮约十分钟，使菌发至全透；大的用
刀对剖成两瓣。猪肥膘肉切成一寸长、三分宽厚的条。

\step 猪油放入大炒锅内置于旺火上烧至七成热，即将鱼头放入稍炸，并烹入料酒，炸至
略呈微黄色时捞出；滗去猪油，留一、二两在锅内，将猪肥膘肉及鸡鸭足、料酒、葱姜放
入煵一下，即加入鸡汤，开锅后撇去浮沫。

\step 用头号铝锅一个，锅底垫上竹篾箅，先将煵过的鸡鸭足在锅中捞出放于篾箅上垫
好，再将锅内鱼头及猪肥膘肉、鸡汤等全部倒入锅内，即加入酱油、红酱油、金钩、白菌
菰等。然后将锅移于微火上慢慢将鱼头烧熟（约三十分钟），即用筷子将鱼肉轻轻拨下，
至鸡汤已经烧到减少三分之二时去掉姜葱、猪肥膘肉、鸡鸭足等不用，再加入冰糖和蒸
好的大蒜；烧至冰糖溶化、汤已浓缩成汁，即盛入大盘内。

\features

鲢鱼肉以细嫩著称，尤以头部为最好。采用此种久烧慢㸆的家常做法，不仅质稠色亮，味
更鲜美。

\footnotetext{
鲢鱼：这里实际上是指鲇鱼，而不是一般池塘养的鲢鱼，但四川人习惯上称鲇鱼为鲢鱼。
这种鱼无鳞，多涎液，身圆口大，而头平扁，刺少肉嫩，颇为鲜美。
}

\end{recipe}

% vim: filetype=tex noautoindent nojoinspaces
% vim: fileencoding=utf-8 formatoptions+=m
% vim: textwidth=78 tabstop=4 shiftwidth=4 softtabstop=4
