% BSD 3-Clause License
%
% Copyright (c) 2023 Quux System and Technology. All rights reserved.
%
% Redistribution and use in source and binary forms, with or without
% modification, are permitted provided that the following conditions are met:
%
% 1. Redistributions of source code must retain the above copyright notice, this
%    list of conditions and the following disclaimer.
%
% 2. Redistributions in binary form must reproduce the above copyright notice,
%    this list of conditions and the following disclaimer in the documentation
%    and/or other materials provided with the distribution.
%
% 3. Neither the name of the copyright holder nor the names of its
%    contributors may be used to endorse or promote products derived from
%    this software without specific prior written permission.
%
% THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS "AS IS"
% AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE
% IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE ARE
% DISCLAIMED. IN NO EVENT SHALL THE COPYRIGHT HOLDER OR CONTRIBUTORS BE LIABLE
% FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL
% DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR
% SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION) HOWEVER
% CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY,
% OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE
% OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
%
\begin{recipe}{炸班指}

\ingredients

\ingredient{猪肥肠头}{三段（约二斤）}
\ingredient{葱白}{一两}
\ingredient{鸡蛋黄}{一个}
\ingredient{盐}{七钱}
\ingredient{生菜}{二两}
\ingredient{酱油}{三钱}
\ingredient{白糖}{四钱}
\ingredient{清汤}{二两}
\ingredient{甜酱}{三钱}
\ingredient{醋}{四钱}
\ingredient{白矾（研细）}{二钱}
\ingredient{菜油}{一斤半耗一两}
\ingredient{姜（去皮）}{三钱五}
\ingredient{花椒}{十余粒}
\ingredient{料酒}{七钱}
\ingredient{水豆粉}{二钱五}
\ingredient{咖喱}{一分}
\ingredient{蒜}{四钱}
\ingredient{香油}{四钱}

\preparation

\step 选用体厚质佳的肥肠头三段，靠近肛门部份切去一圈不用，在清水中加入白矾末，
把肥肠放入，用力揉搓清洗一次，除去粘液涎水；另换清水加盐，同样揉搓清洗两次。即
把肠的里面（有油的一面）翻出来，用刀撕去油上粘的杂质脏物（注意不要撕掉油），再
继续用水清洗。这样两面反复多洗几次，直到肥肠白净涩手，无臭味为止。最后仍把有油
的一面翻到内面去，洗净后放在开水锅内煮一刻钟捞出。再把肠两端用刀修去一分左右，
使之整齐。每段再分别切成两段（共六段）。用大蒸碗盛起，放入清水、盐、葱白三段、
料酒、花椒、姜等佐料，使水淹没过肥肠，上笼用旺火蒸三小时，至肥肠起着皱折为适
合。

\step 葱白用刀切成一寸长段，两头切成细花翻起。甜酱用香油、白糖拌合调匀。大蒜去
皮，切成四分见方、半分厚的片。生菜洗净，用香油、醋少许、蛋黄、白糖、咖喱拌合
（炸班指时才拌）。葱、姜、大蒜分别用刀切成细末，和香油、料酒、清汤、水豆粉、白
糖、醋、酱油等佐料，用碗盛好调匀，成为糖醋汁。

\step 菜油倒入炒锅内烧沸，将蒸好的肥肠取出（要炸时才取，葱、姜等不要），放在盘
内将水滗干，顺着锅边放入锅内，并立即用汤瓢将肠拨横过来，不使两头肠口向着人（因
为肠内有水，刚一下锅要炸几下，溅起来的油容易烫伤人）。炸时要用汤瓢拨动肥肠，以
便炸匀。约五分钟，肠呈金红色，即把油滗去，淋上香油，颠两下即捞出。然后在案板上
用刀把肥肠切成四分厚的圆圈，堆在盘的中间，盘的两端分别放上拌好的生菜和葱酱蒜。
再在炸班指的原锅内将糖醋汁煎热，盛在两个汤杯内，与班指一同上桌。

\features

此菜色泽金红，皮酥里嫩，细软而香，吃时可佐以葱酱蒜，也可以蘸糖醋汁，还可以伴生
菜叶，都各有风味。因肥肠成圆形，似射箭的班指一样，故名。

\end{recipe}

% vim: filetype=tex noautoindent nojoinspaces
% vim: fileencoding=utf-8 formatoptions+=m
% vim: textwidth=78 tabstop=4 shiftwidth=4 softtabstop=4
