% BSD 3-Clause License
%
% Copyright (c) 2023 Quux System and Technology. All rights reserved.
%
% Redistribution and use in source and binary forms, with or without
% modification, are permitted provided that the following conditions are met:
%
% 1. Redistributions of source code must retain the above copyright notice, this
%    list of conditions and the following disclaimer.
%
% 2. Redistributions in binary form must reproduce the above copyright notice,
%    this list of conditions and the following disclaimer in the documentation
%    and/or other materials provided with the distribution.
%
% 3. Neither the name of the copyright holder nor the names of its
%    contributors may be used to endorse or promote products derived from
%    this software without specific prior written permission.
%
% THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS "AS IS"
% AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE
% IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE ARE
% DISCLAIMED. IN NO EVENT SHALL THE COPYRIGHT HOLDER OR CONTRIBUTORS BE LIABLE
% FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL
% DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR
% SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION) HOWEVER
% CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY,
% OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE
% OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
%
\begin{recipe}{清蒸青鳝}

\ingredients

\ingredient{青鳝（十三两）}{一条}
\ingredient{特级清汤}{三斤}
\ingredient{水发竹荪}[\footnotemark]{五朵}
\ingredient{生猪网油}{二两五}
\ingredient{熟猪肥肉}{半斤}
\ingredient{盐}{一钱}
\ingredient{胡椒面}{二分}
\ingredient{料酒}{四钱}
\ingredient{鸡蛋}{二个}
\ingredient{花椒}{数颗}

\preparation

\step 杀鳝：青鳝身上涎水很多，不易捉住。因此，在杀鳝时先在地上铺一堆细炭灰，将
青鳝由水中捞出放入炭灰中，任它在炭灰中爬来爬去粘满炭灰，就无法逃跑了。这时即用
左手按住鳝颈，右手拿一快刀，在鳝鱼眼后端距离约一分处，将鳝头一刀斩下，放尽血
液。然后用水洗净鳝身的炭灰，放在瓦盆中。

\step 去皮：将热水（水温高低，可用手试一试。方法是：用手在水中抓三下，觉得烫
手，但又烫得不很痛时为合适。饮食业叫它“三把水”。因为水温太高时，抓一二下就会烫
手；水温太低则抓五、六下也不致烫手，这是厨师们的实际经验），舀十斤在鳝鱼盆中，
鳝身被水一烫，鳝皮变色了。并且有的地方鳝皮已离鳝肉，再用小刀轻轻地刮去鳝身的青
色外皮，刮后现出一种银白色的油皮，皮上呈现出美丽的花纹（在去皮过程中切勿将油皮
弄破，以免影响外表美观）。

\step 去鳝翅和切段：将鳝平放在案板上，用剪刀将鳝背翅、鳝尾翅、鳝鳃边的拨水翅全
部剪去；然后由尾部起切段，每段长六分；切至鳝段中发现内脏时，便要改变刀法，不能
再一刀切断，须在鳝身四周割一圈，将骨刺割断，但不要伤着内脏和弄破苦胆，再左手抓
着鳝身，右手拿着鳝段向两头一扯，便将内脏抽出鳝段。照此做法，将整个鳝鱼弄成完整
的鳝段。

\step 定碗入笼：用蒸碗一个，先将网油铺于蒸碗中，再将鳝鱼一段一段地立放在网油
上，把料酒、胡椒面、盐和花椒一起拌匀，淋于鳝段上。再将猪肉切成一寸长、一分半厚
的片，放在鳝段之上。用消毒草纸封固碗口，入蒸笼内，用旺火蒸三十分钟即成。再用蒸
碗一个，放入蛋清二个，和冷清汤一起顺着一个方向搅匀，搅至起泡时入蒸笼内蒸十分
钟，成为白色芙蓉蛋。

\step 翻碗上席：将蒸好的青鳝出笼，将特级清汤一斤烧开，舀半斤倒入青鳝蒸碗中，稍
待片刻，滗去清汤，再将锅内下余清汤舀入蒸碗中，再滗去清汤。将青鳝翻扣在大圆盘
中，揭去网油不用，将白芙蓉蛋划成四块，镶于青鳝四周。再将水发竹荪切成六分长的
段，在二汤中汆热，镶于青鳝四周。再将特级清汤放入锅中，加盐、胡椒面、味精、料酒
等烧开、倒入圆盘中上席。

\features

此系汤菜。青鳝肉肥美，特别鲜嫩适口。

\footnotetext{
水发竹荪：竹荪用水发二十分钟，洗净泥砂即成。
}

\end{recipe}

% vim: filetype=tex noautoindent nojoinspaces
% vim: fileencoding=utf-8 formatoptions+=m
% vim: textwidth=78 tabstop=4 shiftwidth=4 softtabstop=4
