% BSD 3-Clause License
%
% Copyright (c) 2023, 2024 Quux System and Technology. All rights reserved.
%
% Redistribution and use in source and binary forms, with or without
% modification, are permitted provided that the following conditions are met:
%
% 1. Redistributions of source code must retain the above copyright notice, this
%    list of conditions and the following disclaimer.
%
% 2. Redistributions in binary form must reproduce the above copyright notice,
%    this list of conditions and the following disclaimer in the documentation
%    and/or other materials provided with the distribution.
%
% 3. Neither the name of the copyright holder nor the names of its
%    contributors may be used to endorse or promote products derived from
%    this software without specific prior written permission.
%
% THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS "AS IS"
% AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE
% IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE ARE
% DISCLAIMED. IN NO EVENT SHALL THE COPYRIGHT HOLDER OR CONTRIBUTORS BE LIABLE
% FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL
% DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR
% SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION) HOWEVER
% CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY,
% OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE
% OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
%
\begin{recipe}[金钱鸡塔]{鸡塔}

\ingredients

\ingredient{鸡脯肉（去皮）}{二两五}
\ingredient{白头韭菜}{二两五}
\ingredient{生猪肥膘肉}{一两二}
\ingredient{盐}{一分}
\ingredient{熟猪肥膘肉}{一方一斤}
\ingredient{醋}{一钱三}
\ingredient{熟瘦火腿}{二钱}
\ingredient{猪油}{一钱}
\ingredient{鸡蛋清}{四个}
\ingredient{清水}{一两}
\ingredient{干豆粉}{三钱}

\preparation

\step 取生鸡脯肉去筋，与生猪肥膘肉分别用刀背捶成茸；将鸡茸放在瓷盆中，加清水调
散拌匀，务使合为一体，再将猪肉茸放盆中调散拌匀，然后放入鸡蛋清二个，左手抓住盆
边，右手用力将各料搅动。搅时要注意顺着一定的方向搅，不能改变方向乱搅，否则便要
出次品或废品。搅至各料合为一体，颜色白而发亮，看不出一点杂质时，加盐，再如前法
搅六七十下。随后加入清水再搅四、五十下，便成为“鸡糁”。

\step 熟肥膘肉切成一分厚，直径一寸二的圆形片二十四片。选用鲜红透亮的瘦火腿，先
切薄片，再切细丝，最后剁成极细的末。白头韭菜去叶不用，将白头切成三分长的段，漂
入清水中。鸡蛋清与干豆粉一起拌匀成为蛋清豆粉。

\step 将熟猪肥膘肉圆片二十四片平铺在大平盘中，用净布一方在沸水内浸透，挤干水轻
轻搌净肥肉上的油汁，再用手指粘蛋清豆粉在肥膘片上厚厚地抹上一层，然后将盆内“鸡
糁”做成直径六分大的圆珠，放在肥膘圆片上，再用手指粘少许凉水将圆珠抹得圆润光
滑，随即用手指取少许火腿末放在圆珠上使它粘稳，便成为鸡塔。

\step 将锅放在炉上烧烫，将鸡塔肥膘向下贴于锅中，烙至肥膘片成金黄色起锅，摆在大
条盘中央。将韭菜白由水中捞出，滤干水放入小碗中，加盐、醋和香油拌匀；摆入盛鸡塔
条盘中的两端，再将余下的香油淋于鸡塔上入席。

\features

川菜有糁、蒙、酿、贴四大烹调法，此菜制法为其中之一种，作为高贵筵席中“八大菜”
之一。形状美观，底黄、顶红、圆珠，颜色鲜艳。吃时酥香脆嫩，味鲜美，为佐酒佳肴。
配鲜菜更别有风味。

\end{recipe}

% vim: filetype=tex noautoindent nojoinspaces
% vim: fileencoding=utf-8 formatoptions+=m
% vim: textwidth=78 tabstop=4 shiftwidth=4 softtabstop=4
