% BSD 3-Clause License
%
% Copyright (c) 2023, 2025 Quux System and Technology. All rights reserved.
%
% Redistribution and use in source and binary forms, with or without
% modification, are permitted provided that the following conditions are met:
%
% 1. Redistributions of source code must retain the above copyright notice, this
%    list of conditions and the following disclaimer.
%
% 2. Redistributions in binary form must reproduce the above copyright notice,
%    this list of conditions and the following disclaimer in the documentation
%    and/or other materials provided with the distribution.
%
% 3. Neither the name of the copyright holder nor the names of its
%    contributors may be used to endorse or promote products derived from
%    this software without specific prior written permission.
%
% THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS "AS IS"
% AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE
% IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE ARE
% DISCLAIMED. IN NO EVENT SHALL THE COPYRIGHT HOLDER OR CONTRIBUTORS BE LIABLE
% FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL
% DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR
% SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION) HOWEVER
% CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY,
% OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE
% OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
%
\begin{recipe}{红烧鸭卷}

\ingredients

\ingredient{公鸭子一只}{二斤半}
\ingredient{大葱}{三钱}
\ingredient{料酒}{六钱}
\ingredient{鸡蛋}{三个}
\ingredient{口蘑}{六钱}
\ingredient{姜}{二钱}
\ingredient{猪肥瘦肉}{半斤}
\ingredient{生猪网油}{一斤}
\ingredient{二汤}{一斤半}
\ingredient{水发玉兰片}{一两五}
\ingredient{干豆粉}{一两五}
\ingredient{酱油}{三钱}
\ingredient{化猪油}{二斤耗二两}
\ingredient{鸡腿}{一只}
\ingredient{鲜小菜}{五两}
\ingredient{盐}{六分}
\ingredient{瘦火腿}{一两五}

\preparation

\step 口蘑用温水泡十五分钟，洗净泥沙和杂质，去脚，切成细丝。玉兰片、火腿分别切
成一寸半长的粗丝。生猪肥瘦肉、鸡腿肉均切成一寸长、四分见方的条方块。网油切成一
寸半宽、二寸长的片。公鸭宰杀，去毛，去肠脏，将鸭头、鸭翅、鸭脚切下砍成块，再将
鸭身上骨头剔净，然后将鸭肉片成一寸半宽、三寸长的薄片约三十片。

\step 鸡蛋三个去壳，连清带黄与豆粉一起拌匀，成为蛋豆粉待用。

\step 将鸭肉一片平铺于平盘中，放入口蘑丝、笋子丝、火腿丝各一根，卷成卷。然后取
生网油一张平铺净盘中，网油上满抹蛋豆粉，包在鸭卷皮面上（鸭卷成长圆筒形，长一寸
半、直径四分）。这样做成三十个。

\step 锅放火炉上，放入猪油烧红，再将鸭卷抹上一层蛋豆粉放入锅内，炸至显牙黄色时
捞出，倒去余油。锅中留油二两，上炉烧红，放入猪肉、鸡腿块、鸭头、鸭翅、鸭脚等煸
炒，再将二汤放入烧开。然后把姜（拍松）、葱、盐、料酒、酱油一起放入搅匀，另用
砂锅一个，将各物舀入砂锅中，其上放入炸好的鸭卷，上炉用微火煨至七分火时，取出鸭
卷，摆在蒸碗中，摆成卍字形，然后将鸡块放在鸭卷上，再将肉块、鸭头、鸭足、鸭翅等
放在鸡块上，蒸碗口用消毒草纸封固，放入蒸笼内蒸三十分钟出笼，撕去碗口草纸，捡去
肉块、鸭头、鸭翅、鸭脚等另作他用，将蒸碗中的鸡块、鸭卷翻扣盘中，揭去蒸碗（鸭卷
盖面，鸡块垫底）。再把砂锅中的原汁用旺火熬酽，加鲜菜淋入盘中鸭卷之上入席。

\features

此菜颜色金黄，吃时肥而嫩，味浓而鲜香，佐酒下饭均宜。

\end{recipe}

% vim: filetype=tex noautoindent nojoinspaces
% vim: fileencoding=utf-8 formatoptions+=m
% vim: textwidth=78 tabstop=4 shiftwidth=4 softtabstop=4
