% BSD 3-Clause License
%
% Copyright (c) 2023 Quux System and Technology. All rights reserved.
%
% Redistribution and use in source and binary forms, with or without
% modification, are permitted provided that the following conditions are met:
%
% 1. Redistributions of source code must retain the above copyright notice, this
%    list of conditions and the following disclaimer.
%
% 2. Redistributions in binary form must reproduce the above copyright notice,
%    this list of conditions and the following disclaimer in the documentation
%    and/or other materials provided with the distribution.
%
% 3. Neither the name of the copyright holder nor the names of its
%    contributors may be used to endorse or promote products derived from
%    this software without specific prior written permission.
%
% THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS "AS IS"
% AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE
% IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE ARE
% DISCLAIMED. IN NO EVENT SHALL THE COPYRIGHT HOLDER OR CONTRIBUTORS BE LIABLE
% FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL
% DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR
% SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION) HOWEVER
% CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY,
% OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE
% OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
%
\begin{recipe}{鸡蒙葵菜}

\ingredients

\ingredient{鸡脯肉}{二两五}
\ingredient{葵菜}{一斤半}
\ingredient{猪肥膘}{一两三}
\ingredient{水豆粉}{二钱}
\ingredient{鸡蛋清}{二个}
\ingredient{盐}{二分五}
\ingredient{猪瘦肉}{二两五}
\ingredient{味精}{二分}
\ingredient{特级清汤}{二斤}

\preparation

\step 鸡脯肉上的一层白膜用刀片去，用刀背捶成茸，边捶边用刀尖剔尽肉内细筋，再用
刀剁两次（使鸡脯剁成极细的茸）。猪肥膘用刀剁成细泥如油脂状。鸡蛋清及鸡茸倒在碗
内，用竹筷使力向着一定方向不间歇地搅打十分钟，要搅散搅匀，直到把它滴一点在水面
上不沉底为止。这时分五次加入清水一两，边加边搅。搅匀后再放入盐、水豆粉，再同样
搅匀；而后又加入肥膘泥，继续搅匀成稀糊状。把瘦肉捶成茸，盛入碗内，用清水调散待
用。

\step 葵菜（冬苋菜）淘洗干净，把菜心（苞）连嫩茎掐下四十朵，再淘洗后用清水泡约
五分钟，捞出再换水洗一次（主要洗净菜的泥沙杂物）。洗净后把菜心倒入开水锅内，待
水重开，菜刚熟即用漏瓢捞入清水内冷透。随即捞出挤干水，抖散，用刀把每根葵菜修成
一寸长，使之整齐，摆在盘内。

炒锅放入清水，烧至七成开时（水冒起鱼眼睛泡时），即将盘内葵菜逐一用手在稀糊状的
鸡茸内裹一层鸡茸，一朵一朵放入锅内，葵菜放完水已全开，鸡茸则全蒙在菜上，随即把
锅端离火口。

\step 将另一炒锅放入清汤烧开，加入盐，把调散的肉茸水一半倒入，用汤瓢在炒锅搅一
转，汤面则浮一层肉沫，即将锅端离火口一半，使锅内汤成半开状，浮沬则逐渐集中，随
用漏瓢撇去浮沫，再把锅放回原处，倒入剩下的一半肉茸，开锅后同样撇去浮沫。此时汤
已变得清彻如白水，即将蒙好的葵菜用漏瓢捞入汤内煮一下，加味精后倒入碗内即成。

\features

此菜汤色清亮，菜嫩汤鲜，清爽可口，特别适宜于老年人食用。

\end{recipe}

% vim: filetype=tex noautoindent nojoinspaces
% vim: fileencoding=utf-8 formatoptions+=m
% vim: textwidth=78 tabstop=4 shiftwidth=4 softtabstop=4
