% BSD 3-Clause License
%
% Copyright (c) 2023 Quux System and Technology. All rights reserved.
%
% Redistribution and use in source and binary forms, with or without
% modification, are permitted provided that the following conditions are met:
%
% 1. Redistributions of source code must retain the above copyright notice, this
%    list of conditions and the following disclaimer.
%
% 2. Redistributions in binary form must reproduce the above copyright notice,
%    this list of conditions and the following disclaimer in the documentation
%    and/or other materials provided with the distribution.
%
% 3. Neither the name of the copyright holder nor the names of its
%    contributors may be used to endorse or promote products derived from
%    this software without specific prior written permission.
%
% THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS "AS IS"
% AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE
% IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE ARE
% DISCLAIMED. IN NO EVENT SHALL THE COPYRIGHT HOLDER OR CONTRIBUTORS BE LIABLE
% FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL
% DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR
% SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION) HOWEVER
% CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY,
% OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE
% OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
%
\begin{recipe}{蝴蝶竹荪}

\ingredients

\ingredient{竹荪}{四钱}
\ingredient{鸡蛋}{五个}
\ingredient{鲜鱼肉}{四两}
\ingredient{肥膘肉}{二两}
\ingredient{鲜笋}{二两}
\ingredient{熟火腿}{一两}
\ingredient{黑芝麻}{一钱}
\ingredient{干豆粉}{五钱}
\ingredient{盐}{七分}
\ingredient{味精}{三分}
\ingredient{胡椒面}{二分}
\ingredient{料酒}{五钱}
\ingredient{酱油}{二钱}
\ingredient{猪瘦肉}{三两}
\ingredient{鸡脯肉}{三两}
\ingredient{清汤}{一斤半}
\ingredient{丝瓜}{三两}

\preparation

\step 将竹荪用温水泡胀，换清水洗数次，放在墩子上用刀修去两头，剖开成为六分宽、
二寸长的片子，共四十八片；将片的同一方向的两头修去呈半圆形，共修二十四片，余下
的二十四片用斜刀切断呈箭头形；将四十八片竹荪一并放入沸水内汆过，滗去清水，用好
汤煨一次，放入碗内装好待用。

\step 鸡蛋摊成蛋皮；鲜笋煮熟放在碗内；丝瓜刮后车下皮，洗净，切成二寸长的段，用
沸水泹熟，用清水漂起；再将丝瓜皮、蛋皮、鲜笋、火腿切成二寸长的二粗丝，分开装入
盘内。黑芝麻淘洗干净，捞起；半个蛋清拌成蛋清豆粉；鲜鱼肉去净皮、翅，用刀背反复
捶茸（肉内不见籽为准）；肥膘剁细（如油脂）。再将鱼茸放入瓢内，三个半蛋清，八钱
清水，三分盐、剁好的肥膘茸及水发湿的干豆粉打成“鱼糁”装入碗内待用。

\step 将修去边角的竹荪摆成蝴蝶形，中间抹上蛋清豆粉，再将鱼糁刮于手心上呈尖刀
形，约一寸五长，放于抹豆粉处，二十四个照样摆完。再用铁夹将丝瓜、火腿、蛋皮丝各
夹一丝入糁的中心，夹二根单丝插入糁的前面，放二粒芝麻在糁的上边，二十四个一起做
完即为蝴蝶竹荪。上笼蒸五分钟即熟（用时馏热）。鸡脯肉、猪瘦肉分别捶成茸子，并用
清水澥散，装入碗内。

\step 将锅放在旺火上，倒下一斤半清汤加酱油、胡椒、盐，烧开后投入红茸子，推动数
转，微开时打尽肉沫；再投入白茸子，推动数转，微开时，同样打尽肉沫，无杂质时，放
下味精，取出笼内的蝴蝶竹荪，用清汤过一次，翻入大汤盘内，再将锅内的清汤灌入即
成。

\features

形色美丽，汤鲜味美，适宜春夏二季。

\end{recipe}

% vim: filetype=tex noautoindent nojoinspaces
% vim: fileencoding=utf-8 formatoptions+=m
% vim: textwidth=78 tabstop=4 shiftwidth=4 softtabstop=4
