% BSD 3-Clause License
%
% Copyright (c) 2023 Quux System and Technology. All rights reserved.
%
% Redistribution and use in source and binary forms, with or without
% modification, are permitted provided that the following conditions are met:
%
% 1. Redistributions of source code must retain the above copyright notice, this
%    list of conditions and the following disclaimer.
%
% 2. Redistributions in binary form must reproduce the above copyright notice,
%    this list of conditions and the following disclaimer in the documentation
%    and/or other materials provided with the distribution.
%
% 3. Neither the name of the copyright holder nor the names of its
%    contributors may be used to endorse or promote products derived from
%    this software without specific prior written permission.
%
% THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS "AS IS"
% AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE
% IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE ARE
% DISCLAIMED. IN NO EVENT SHALL THE COPYRIGHT HOLDER OR CONTRIBUTORS BE LIABLE
% FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL
% DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR
% SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION) HOWEVER
% CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY,
% OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE
% OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
%
\begin{recipe}[菠饺银肺]{菠饺白肺}

\ingredients

\ingredient{猪肺一副}{约二斤}
\ingredient{盐}{一两五}
\ingredient{姜}{二分}
\ingredient{面粉}{二两五}
\ingredient{酱油}{一钱五}
\ingredient{化猪油}{一两}
\ingredient{猪肉（肥瘦）}{二两五}
\ingredient{清汤}{二斤}
\ingredient{鸡油}{一钱}
\ingredient{熟火腿}{六钱}
\ingredient{菠菜}{二斤}
\ingredient{味精}{二分}
\ingredient{水发口蘑}{六钱}
\ingredient{料酒}{五钱}
\ingredient{香油}{一钱}
\ingredient{熟鸡皮}{六钱}
\ingredient{葱白}{三钱}
\ingredient{胡椒面}{二分}

\preparation

\step 选择较白净无破洞的猪肺一副（可先检查，看是否有漏气的地方），用绳将肺把子
拴住，肺叶向下挂起，用大铁壶盛清水（有自来水的就用自来水龙头）慢慢由肺上端管口
灌入冲洗，待肺内水满膨胀，即用双手轻轻捧起肺叶向上倾倒一次血水。灌时若遇血块阻
塞停滞，可用一比肺管口略细、长约七寸的竹管插入肺管内用手轻拍，使之畅通再灌（但
不能用力过大，不然肺易破裂，裂后就不能洗白了）。这样反复灌洗，到肺内红色血水全
部随水漫出，猪肺全部变为白色为止。冲洗净后，把肺叶向上肺管向下用竹筲箕装起，将
水滤干，再照原来方法把肺挂起，滤净水，入沸水锅中煮熟，切成长一寸二分、宽一寸、
厚半分的片。

\step 猪肉去筋，在菜墩上用刀剁成细泥，加入香油、盐、冷清汤在碗内拌合成馅。火
腿、鸡皮切成一寸二分长、八分宽的片待用。

\step 菠菜淘洗干净，去茎留叶，在木瓢内用手搓揉成菜泥，用纱布包好挤出绿色菜汁，
和入干面粉内拌匀（汁不够时可略加清水）用力揉成面团；再平均扯成二十四个小面剂，
用小面棍擀成圆形饺皮。把拌好的馅分摊在饺皮上对折包成半圆形，饺边用手捏成细折，
然后用清水把饺子煮好，端离火口，用时再捞出。

\step 猪油放在炒锅内，于旺火上烧热，放入姜、葱白、料酒和清汤，开锅后用漏瓢将
姜、葱捞出不用，放入盐、胡椒面、味精，同时捞起锅内的水饺倒入汤锅内，再加入口
蘑、火腿、鸡皮、白肺片，至汤再开后淋入鸡油倒入大菜盘内即成。

\features

此菜用料平常，但烹制精细，不仅汤内饺子碧绿，肺片银白，两色相间，颜色美观，而且
菜的质地亦非常细嫩鲜美。“菠饺”在川菜中应用很广。如“菠饺海参”、“菠饺鱿鱼”
等等，均可如法炮制。

\end{recipe}

% vim: filetype=tex noautoindent nojoinspaces
% vim: fileencoding=utf-8 formatoptions+=m
% vim: textwidth=78 tabstop=4 shiftwidth=4 softtabstop=4
