% BSD 3-Clause License
%
% Copyright (c) 2023--2025 Quux System and Technology. All rights reserved.
%
% Redistribution and use in source and binary forms, with or without
% modification, are permitted provided that the following conditions are met:
%
% 1. Redistributions of source code must retain the above copyright notice, this
%    list of conditions and the following disclaimer.
%
% 2. Redistributions in binary form must reproduce the above copyright notice,
%    this list of conditions and the following disclaimer in the documentation
%    and/or other materials provided with the distribution.
%
% 3. Neither the name of the copyright holder nor the names of its
%    contributors may be used to endorse or promote products derived from
%    this software without specific prior written permission.
%
% THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS "AS IS"
% AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE
% IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE ARE
% DISCLAIMED. IN NO EVENT SHALL THE COPYRIGHT HOLDER OR CONTRIBUTORS BE LIABLE
% FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL
% DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR
% SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION) HOWEVER
% CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY,
% OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE
% OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
%
\begin{recipe}{鱼香茄饼}

\ingredients

\ingredient{茄子}{六两}
\ingredient{盐}{三分}
\ingredient{味精}{二分}
\ingredient{肥瘦肉}{三两}
\ingredient{姜末}{二钱五}
\ingredient{红泡辣椒}{一两}
\ingredient{火腿}{六钱}
\ingredient{蒜末}{二钱五}
\ingredient{豆粉}{六钱}
\ingredient{净鲜笋}{一两}
\ingredient{料酒}{八钱}
\ingredient{清汤}{二两五}
\ingredient{金钩}{三钱}
\ingredient{酱油}{六钱}
\ingredient{菜油}{二斤耗四两}
\ingredient{鸡蛋清}{二个}
\ingredient{醋}{五钱}
\ingredient{干豆粉}{一两}
\ingredient{白糖}{三钱}

\preparation

\step 鲜嫩茄子去皮削成直径一寸三分的圆柱状，再切成三分厚的片三十六片，净重四
两。选用大膘猪的背柳肉二两，肥膘一两，混合剁成肉末。金钩用沸水泡一小时，再用温
水洗二三次，与火腿、鲜笋分别剁碎如小米粒大。大碗内放入酱油、盐、味精、水豆
粉，加清水调匀，再加料酒，与猪肉末、金钩末、火腿末、鲜笋末等一并用竹筷搅匀，成
为混合肉末。

\step 将鸡蛋清和干豆粉一起用竹筷搅匀，再加入盐调成蛋清豆粉。

\step 将茄片逐片平放在菜墩上，用刀均匀地片为两片，进刀深度一寸，留三分相连。分
别酿入混合肉末成酿茄片。

\step 菜油舀入锅中，放在旺火上烧至微冒烟时，即移微火上；然后用手逐一将酿茄片立
着在蛋清豆粉中滚一转，粘上封口处，随即放入油锅中炸；要边粘边炸，不可全部粘好再
炸，否则易裂口；待茄片炸至周边呈金黄色即捞起，边炸边捞。全部炸完后，把余下蛋清
豆粉加入清水少许调匀，将茄饼放入，用手从下向上轻轻翻转，把蛋清豆粉沾裹完，再放
入油中炸成金黄色捞起，滤尽油，摆入盘中。

\step 锅内滗去余油，留油一两半放在旺火上，待油冒烟时下姜、蒜末，炒香，随将酱
油、盐、水豆粉、料酒、味精、白糖、泡红辣椒末（将泡辣椒剁成极细碎末）等放在一个
碗内，将清汤一同倾入锅中，烧至汤浓缩冒大泡时，放入葱末，起锅淋在茄饼上即成。

\features

此菜颜色金红，味甜酸，外酥内鲜，别具风味。

\end{recipe}

% vim: filetype=tex noautoindent nojoinspaces
% vim: fileencoding=utf-8 formatoptions+=m
% vim: textwidth=78 tabstop=4 shiftwidth=4 softtabstop=4
