% BSD 3-Clause License
%
% Copyright (c) 2023, 2024 Quux System and Technology. All rights reserved.
%
% Redistribution and use in source and binary forms, with or without
% modification, are permitted provided that the following conditions are met:
%
% 1. Redistributions of source code must retain the above copyright notice, this
%    list of conditions and the following disclaimer.
%
% 2. Redistributions in binary form must reproduce the above copyright notice,
%    this list of conditions and the following disclaimer in the documentation
%    and/or other materials provided with the distribution.
%
% 3. Neither the name of the copyright holder nor the names of its
%    contributors may be used to endorse or promote products derived from
%    this software without specific prior written permission.
%
% THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS "AS IS"
% AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE
% IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE ARE
% DISCLAIMED. IN NO EVENT SHALL THE COPYRIGHT HOLDER OR CONTRIBUTORS BE LIABLE
% FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL
% DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR
% SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION) HOWEVER
% CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY,
% OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE
% OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
%
\begin{recipe}{锅贴豆腐}

\ingredients

\ingredient{石膏豆腐}{六块}
\ingredient{猪肥膘肉}{七两五}
\ingredient{鸡蛋}{三个}
\ingredient{干豆粉}{四钱}
\ingredient{味精}{二分}
\ingredient{番茄酱}{六钱}
\ingredient{生菜}{二两}
\ingredient{盐}{二分}
\ingredient{面粉}{二分}
\ingredient{熟瘦火腿}{三钱}
\ingredient{化猪油}{二两}
\ingredient{香油}{三钱}
\ingredient{醋}{三钱}
\ingredient{白糖}{三钱}

\preparation

\step 猪肥膘肉在汤锅内煮八分熟，捞出晾冷，切成一寸二长、一寸宽、一分厚的片二十
四片，用刀尖在每片的四角及中心轻轻划穿（这样贴时肉片才不会卷起）。生豆腐放入丝
箩内搅散、滤去渣，取豆腐汁装入碗内。鸡蛋清用竹筷在八寸盘内用力向着一个方向快速
搅打，搅打至全部变为雪白成团的细泡，将筷子一支插入细泡内不倒时为止。把盐、干豆
粉、面粉、味精和鸡蛋泡都加入豆腐汁的碗内，搅匀后再加入化猪油搅匀，成为“豆腐
糁”。用鸡蛋清与干豆粉调成蛋清豆粉。

\step 熟肥猪肉片二十四片分开摊在盘内，用拧干的热布帕把油搌干，将每个肉片上抹上
一层蛋清豆粉；再用调羹将豆腐糁舀在上面，平摊约三分厚（四边稍薄，贴时才不会
流）。鸡蛋黄（三个）搅散，倒入猪油抹过的炒锅内（用猪油很少，使蛋不巴锅即可），
于旺火上摊成蛋皮。蛋皮及痩火腿先各切成细丝，再切成细末，按在摊好的豆腐糁上，每
片放上火腿及蛋皮末各一半，然后在盘内摆好，上笼蒸约五分钟即熟，取出。

\step 炒锅放在旺火上烧至七成热，倒入猪油将锅转动，使锅内粘上一层油，即滗去油，
随将蒸好的豆腐（肥肉片向下）逐个贴在锅内约煎八分钟。煎时将锅左右前后移动，以免
煳锅。煎至肉底呈现金黄色、豆腐呈浅黄色时，淋入香油，将炒锅转动一下即起锅。把有
火腿末的一面向上摆在盘的一端；将淘洗干净的生菜掐叶去根（长约一寸二分），用糖、
醋、香油拌合好后放在盘的另一端；然后将番茄酱淋在生菜面上即成。

\features

此菜在浅黄色豆腐上微微透出火腿及蛋黄皮的红黄两色，镶以绿色生菜，色调美观，食
之松脆香嫩清爽可口。

\end{recipe}

% vim: filetype=tex noautoindent nojoinspaces
% vim: fileencoding=utf-8 formatoptions+=m
% vim: textwidth=78 tabstop=4 shiftwidth=4 softtabstop=4
