% BSD 3-Clause License
%
% Copyright (c) 2023 Quux System and Technology. All rights reserved.
%
% Redistribution and use in source and binary forms, with or without
% modification, are permitted provided that the following conditions are met:
%
% 1. Redistributions of source code must retain the above copyright notice, this
%    list of conditions and the following disclaimer.
%
% 2. Redistributions in binary form must reproduce the above copyright notice,
%    this list of conditions and the following disclaimer in the documentation
%    and/or other materials provided with the distribution.
%
% 3. Neither the name of the copyright holder nor the names of its
%    contributors may be used to endorse or promote products derived from
%    this software without specific prior written permission.
%
% THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS "AS IS"
% AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE
% IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE ARE
% DISCLAIMED. IN NO EVENT SHALL THE COPYRIGHT HOLDER OR CONTRIBUTORS BE LIABLE
% FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL
% DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR
% SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION) HOWEVER
% CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY,
% OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE
% OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
%
\begin{recipe}{红烧甲鱼}

\ingredients

\ingredient{甲鱼}{约二斤}
\ingredient{化猪油}{一两五}
\ingredient{味精}{三分}
\ingredient{猪肉}{半斤}
\ingredient{姜}{四钱}
\ingredient{胡椒面}{一分}
\ingredient{鸡翅八个}{约五两}
\ingredient{葱白}{四钱}
\ingredient{清汤}{一斤三两}
\ingredient{独蒜}{二两}
\ingredient{盐}{六分}
\ingredient{鸡汤}{二斤}
\ingredient{料酒}{六钱}
\ingredient{酱油}{七钱}
\ingredient{鸡油}{三钱}
\ingredient{咸红酱油}{三钱}

\preparation

\step 猪肉选用五花的，洗净切成块；鸡翅膀切去翅尖，砍为两段；猪肉与鸡翅一同用沸
水在锅内汆五分钟，除尽浮沫后捞出。将锅置于旺火上，放入猪油和一块拍松的姜、葱白
段，再放入猪肉、鸡翅，一并煸四、五分钟，加红、白酱油和盐，再烹入料酒，加入鸡汤
烧沸，倒入砂锅盖好，放在偏火眼上，焅着即为老汤。净大蒜装盘上笼蒸𤆵。

\step 将甲鱼平放在菜墩上，腹部向上，头即伸出，等头伸出后一刀斩断，放净血；锅内
水烧沸，将甲鱼放入汆约十分钟（用手指甲能刮掉裙边上的粗皮为度，过久或不够火候都
不易刮掉，汆的时间可视甲鱼的老嫩而增减。）捞起，用小刀将甲鱼壳周围的裙边、腹部
软皮与四肢粗皮刮净，再入沸水中汆约十五分钟，去掉脊上甲壳和内脏，用清水洗净，切
去足爪，横砍成二寸长的块。用沸水汆约五分钟后，在清水中漂约十五分钟，然后再用清
汤加姜和葱白段，用微火汆约八分钟，去其泥腥味。捞出后（汆汤不用）放入煨有猪肉和
鸡翅的“老汤”锅内煨十分钟，至甲鱼肉𤆵透，汤汁约余四两左右时，即倒入锅中，将猪肉
块取出另作他用，鸡翅放在盘中心。然后将锅放在旺火上，将大蒜从笼内取出放入，用汤
瓢轻轻翻搅，等滋汁浓缩约二两多时，加入胡椒面、味精，淋入鸡油造匀，倒在盘中鸡翅
上，再用竹筷将裙边拈在面上即成。

\features

此菜色泽金黄，味浓而鲜美，肉𤆵可口，富于营养。但须注意甲鱼肉不可与苋菜同食。

\end{recipe}

% vim: filetype=tex noautoindent nojoinspaces
% vim: fileencoding=utf-8 formatoptions+=m
% vim: textwidth=78 tabstop=4 shiftwidth=4 softtabstop=4
