% BSD 3-Clause License
%
% Copyright (c) 2023 Quux System and Technology. All rights reserved.
%
% Redistribution and use in source and binary forms, with or without
% modification, are permitted provided that the following conditions are met:
%
% 1. Redistributions of source code must retain the above copyright notice, this
%    list of conditions and the following disclaimer.
%
% 2. Redistributions in binary form must reproduce the above copyright notice,
%    this list of conditions and the following disclaimer in the documentation
%    and/or other materials provided with the distribution.
%
% 3. Neither the name of the copyright holder nor the names of its
%    contributors may be used to endorse or promote products derived from
%    this software without specific prior written permission.
%
% THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS "AS IS"
% AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE
% IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE ARE
% DISCLAIMED. IN NO EVENT SHALL THE COPYRIGHT HOLDER OR CONTRIBUTORS BE LIABLE
% FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL
% DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR
% SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION) HOWEVER
% CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY,
% OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE
% OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
%
\begin{recipe}{生片菊花锅}

\ingredients

\ingredient{鲫鱼}{八两}
\ingredient{胡椒}{三分}
\ingredient{粉条}{二钱}
\ingredient{油炸花生米}{一两五}
\ingredient{生鸡脯肉}{三两}
\ingredient{盐}{三分}
\ingredient{豌豆尖}{三两}
\ingredient{油条}{三根}
\ingredient{奶汤}{二斤半}
\ingredient{香菜}{一两}
\ingredient{干粉}{五钱}
\ingredient{菜油}{一斤耗三两}
\ingredient{葱}{二钱}
\ingredient{白菜心}{三两}
\ingredient{鸡𬂁肝}{三个}
\ingredient{味精}{三分}
\ingredient{菠菜}{五两}
\ingredient{猪腰}{四两}
\ingredient{化猪油}{一两}
\ingredient{姜}{二钱}
\ingredient{粗撒子}{二把}
\ingredient{白菊花}{一朵}

\preparation

\step 鲫鱼洗净，去鳞，去肠杂，去刺（刺留用），用刀切成二寸长、一分厚、宽同鱼身
的薄片。鸡𬂁肝洗净，去表皮，切成薄片。生鸡脯肉片为一寸长、八分宽的薄片。猪腰去
筋和腰臊，切成鸡脯大小的薄片（以上薄片，愈薄愈好）。这四种片称为“四生片”，分别
摆于七寸盘中成风车形。

\step 菜油一斤入锅烧红，投入粉条，炸成黄色；花生米去皮；油条切成一寸长段；撒子
捏散（临上席时再用油炸一次以保持酥脆）；分别放入七寸盘内，称为“四油酥”。

\step 白菜心洗净，用手撕去筋；豌豆尖淘洗，只留嫩苞；菠菜去老叶和茎根部分；香菜
洗净；分别放于七寸盘中，称为“四鲜菜”。

\step 姜一钱去皮，切成细末；葱切成葱花；与胡椒、味精共摆一碟，每样占碟的四分之
一。另以小碟盛盐备用。

\step 鲜菊花一大朵（最好为自色），用刀切去花蒂，抽出花蕊，仍以菊花原形放入盘
中。

\step 锅置火上，放入猪油，加入姜（拍松）、葱切成五分长的短节，随即放入奶汤和鱼
骨刺，烧沸，约五分钟捞去鱼骨刺和姜、葱，把汤舀入铜锅内为鱼羹汤。

\step 桌上放一粗瓷深盘，盘内盛酒精，盘上加铜架，架上放铜锅，吃时将酒精燃烧，锅
内汤沸时先将菊花放下，次将各类生肉、生菜分别于汤内烫熟吃（除生片、生菜外其余油
酥忌下锅内）。

\features

此菜宜于秋季吃，生片、鲜菜汤味清鲜，佐酒下饭均宜。菜内生片、鲜菜可按季节变动，
但只能用四样。冬季改用梅花，即名“梅花锅”。

\end{recipe}

% vim: filetype=tex noautoindent nojoinspaces
% vim: fileencoding=utf-8 formatoptions+=m
% vim: textwidth=78 tabstop=4 shiftwidth=4 softtabstop=4
