% BSD 3-Clause License
%
% Copyright (c) 2023 Quux System and Technology. All rights reserved.
%
% Redistribution and use in source and binary forms, with or without
% modification, are permitted provided that the following conditions are met:
%
% 1. Redistributions of source code must retain the above copyright notice, this
%    list of conditions and the following disclaimer.
%
% 2. Redistributions in binary form must reproduce the above copyright notice,
%    this list of conditions and the following disclaimer in the documentation
%    and/or other materials provided with the distribution.
%
% 3. Neither the name of the copyright holder nor the names of its
%    contributors may be used to endorse or promote products derived from
%    this software without specific prior written permission.
%
% THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS "AS IS"
% AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE
% IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE ARE
% DISCLAIMED. IN NO EVENT SHALL THE COPYRIGHT HOLDER OR CONTRIBUTORS BE LIABLE
% FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL
% DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR
% SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION) HOWEVER
% CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY,
% OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE
% OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
%
\begin{recipe}[八宝全鸭]{糯米全鸭}

\ingredients

\ingredient{肥鸭一只}{三斤}
\ingredient{糯米}{二两}
\ingredient{湘莲子}{一两五}
\ingredient{芡实}{九钱}
\ingredient{苡仁}{九钱}
\ingredient{熟火腿}{一两五}
\ingredient{金钩}{二钱}
\ingredient{扁豆仁}{九钱}
\ingredient{口蘑}{九钱}
\ingredient{盐}{一钱五}
\ingredient{料酒}{四钱}
\ingredient{胡椒面}{二分五}
\ingredient{菜油}{二斤耗一两}
\ingredient{草碱}{一钱}

\preparation

\step 湘莲子放入碗中，倒入草碱和匀，渍五分钟然后加水倒入锅中，放炉火上烧至水快
开时，用刷把戳去莲子皮，捞出放入清水中，再用手搓去余皮；随后削去顶蒂，抽去心。
扁豆淘洗干净，加水倒入锅中煮十五分钟，剥去皮。糯米淘洗干净，用清水漂五分钟。苡
仁、芡实去净杂质，用温水泡十五分钟。金钩加温水浸透使发胀。口蘑用温水泡十分钟，
淘净泥沙，掐去足，用刀切成三分方丁。选用去皮肥瘦火腿，同样切成三分方丁。以上八
种原料，分别去干水份，一起放入大碗中，加料酒、盐、胡椒面拌匀，上笼蒸三十分钟出
笼，称为“八宝”。

\step 鸭子宰杀后，去毛，洗净，切去足；将鸭放于案板上，在鸭颈上（鸭胸上两寸处）
顺着颈项开一口，长约二寸半；在咽喉刀口处切断颈颡骨，使鸭头与鸭皮整个相连；再从
刀口处剔出项骨。然后将鸭子尾部向下立放案板上，将鸭皮连肉翻着往下退，同时从颈颡
骨尽头处开始用刀剔除骨头，一直剔到鸭尾；除两翅不剔骨外，其余骨头须全部剔出不用
（在剔骨过程中必须保持鸭肉的完整，不要弄破鸭皮）。然后将鸭翻过来（因为在剔骨时
鸭皮翻在里面，肉在外面，故须翻过来），使鸭皮朝外，成为一只无骨的完整全鸭。再从
蒸笼内取出八宝掐全部装入鸭腹内，在刀口处将鸭颈皮打一个结，以免腹中的馅漏出。然
后放入汤锅中烫三分钟后捞出，再入清水中，摘尽茸毛。用料酒、盐、胡椒面等和匀，抹
满鸭的全身。将鸭腹朝下，鸭背向上放于大蒸碗中，鸭头放于鸭背两翅的中间，上笼蒸一
点半钟，出笼晾干水气。

\step 菜油在锅内烧至将见油烟时，将鸭子放入油中炸五分钟，炸至皮酥，并呈金黄色时
起锅。将鸭照原形摆入盘中上席。

\features

此菜色泽金黄，形如全鸭、大方美观，外酥内𤆵，属席桌大菜之一。

\end{recipe}

% vim: filetype=tex noautoindent nojoinspaces
% vim: fileencoding=utf-8 formatoptions+=m
% vim: textwidth=78 tabstop=4 shiftwidth=4 softtabstop=4
